The Shape and Color of Politics

### 2023-09-27 chapter_2/src/slides/slides.qmd
update slides

@@

[![1860s Ballots](../../assets/slides/imgs/ballots.avif){#fig-ballots width=6.5in}](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)

@@

[![Democratic National Convention](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem width=6.5in}](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)

[![Republican National Convention](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep width=6.5in}](https://reuther.wayne.edu/node/9207)

@@

[![2000 Presidential Election map](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)

@@

[![The public](../../assets/slides/imgs/division.webp){#fig-public width=6.5in}](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)

>>>>

## Follow-along

![QR Code](../../assets/slides/imgs/qr-code.png){#fig-qr}

@@

![[1860s Ballots](https://slate.com/news-and-politics/2020/02/ballot-history-photo-essay.html)](../../assets/slides/imgs/ballots.avif){#fig-1860-ballot}

@@

![[Democratic National Convention](https://untappedcities.com/2021/08/12/1980-democratic-national-convention/)](../../assets/slides/imgs/1980_dem_convention.jpg){#fig-1980-dem width=6.5in}

![[Republican National Convention]((../../assets/slides/imgs/1980_rep_convention.jpg))](../../assets/slides/imgs/1980_rep_convention.jpg){#fig-1980-rep width=6.5in}

@@

![[2000 Presidential Election Map](https://www.google.com/url?sa=i&url=https%3A%2F%2Fwww.smithsonianmag.com%2Fhistory%2Fwhen-republicans-were-blue-and-democrats-were-red-104176297%2F&psig=AOvVaw3mlqWWKalyCl0gzVJDCIV5&ust=1694829600914000&source=images&cd=vfe&opi=89978449&ved=0CA8QjRxqFwoTCJCNg7bCq4EDFQAAAAAdAAAAABAT)](../../assets/slides/imgs/2000_election_map.webp){#fig-2000-election-map width=6.5in}

@@

![[The public](https://www.brookings.edu/articles/what-is-a-brokered-convention-what-is-a-contested-convention/)](../../assets/slides/imgs/division.webp){#fig-public width=6.5in}
